---
title: "Stocks"
format:
  html:
    code-link: true
    code-fold: true
editor: visual
execute:
  keep-md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

# Load the required libraries
library(ggplot2)
library(tidyverse)
library(tidyquant)
library(dygraphs)
library(ggforce)
library(lubridate)
library(timetk)
library(rmarkdown)
library(forecast)
```
I wanted to predict what our retirement would look like with the stocks we've picked when my wife and I got married. These are the top 5 stocks that I've handpicked when we started investing. 

However, like most stock analysis predictions, using statistics and math to produce models is not 100% reliable. Complexity of Financial Markets and Randomness and Uncertainty will always play a role in the voilatility to the market. Thus, this is not a financial advice! 
```{r}

# Pull 5 stock picks my wife and I have.

df <- tq_get(c("NVDA", "VTI", "AAPL", "SCHD", "IBM"),
             get = "stock.prices",
             from = "2017-12-01",
             to = "2023-09-26") # Date can be modified to pick the current date end_date for this demo I want to select the date I finished this project

# Data Wrangling 
df2 <- df %>% pivot_wider(names_from = symbol, values_from = adjusted, id_cols = date)

xts <- df2 %>%
  tk_xts(date = date)

stocks <- dygraph(xts, main = "Tech Stocks", xlab = "Years", ylab = "Stock Prices") %>%
  dyRangeSelector(dateWindow = c("2017-12-01", "2023-09-26"))

# Display the dygraph
stocks

# Forecast for the next year
forecast_period <- 7305  #20 years

# Function to create a forecast for a stock
create_forecast <- function(symbol) {
  symbol_data <- xts[, symbol]
  symbol_ts <- ts(symbol_data, frequency = 7305)
  
  forecast_model <- forecast(auto.arima(symbol_ts))
  
  plot(forecast_model, main = paste("Forecast for", symbol), xlab = "Years", ylab = "Stock Prices")
}

# Create and display forecasts for each stock
for (symbol in colnames(xts)) {
  create_forecast(symbol)
}
```
